Non-exclusive Characteriazations of Demands and Resources across O*NET Job Elements

### 2024-08-02 Submission.Rmd
Updating the paper per journal editor request in preparation for review.

>>>>

The next group of hypotheses focuses on the relationship among resources and demands (challenge and hindrance) and outcomes. Table 2 shows the overall associations between resource/challenge/hindrances and outcomes of engagement, stress, and burnout. Here, we observe positive associations between resources, and challenges with engagement, and a negative association between hindrances and engagement. A positive association is observed between hindrances and stress.
